---
title: "Exercise: Data Analysis Workflow"
author: "Yuan Chai"
date: '2022-09-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise: Farm Data Analysis 

In this exercise, you will work through a typical data analysis workflow using the `02_df_farm_v2.csv` data file we created in class. In this exercise, you will explore the differences in fertilizer use and farm yield among rich, mid, and poor income countries.

Follow this general template, write your own code and modify as needed to document your own work.

## Workspace setup

### Start with a clean workspace

```{r}

```

### Load packages

```{r}

```

## Import Data

### Import data from files

```{r}
# import file "./data/02_dat_farm_v2.csv"

```

### Create new datasets

```{r}
# create a new dataframe with data only from rich country

# create a new dataframe with data only from mid income country

# create a new dataframe with data only from poor income country

```

### Summary statistics

```{r}
# dataframe structure

```

```{r}
# Use the stargazer function to generate well-formated summary statistics

```

## Simple plots

```{r}
# Histogram for rich country

# Histogram for mid income country

# Histogram for poor country

```

```{r}
# Scatterplots


```

## Simple regression

### OLS

```{r}
# Run OLS separately for thress income groups

```

## Export results

Since we created new variables, we might wish to save the new datasets into new csv files

```{r}
# Write data to csv file

```

Write summary statistics into txt file

```{r}
# Data summary statistics

```

Write the regression table into txt file

```{r}
# Regression results

```
