---
title: "Exercise: Data Analysis Workflow"
author: "Yuan Chai"
date: '2023-10-02'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise: Farm Data Analysis

In this exercise, you will work through a typical data analysis workflow using the `02_df_farm_v2.csv` data file we created in class. In this exercise, you will explore the differences in fertilizer use and farm yield among high, mid, and low income countries.

Follow this general template, write your own code and modify as needed to document your own work.

## Workspace setup

### Start with a clean workspace

```{r}
# use rm(list=ls()) to clear up the worksapce environment

```

### Load packages

```{r}
# load the stargazer package

```

## Import Data

### Import data from files

```{r}
# create a dataframe dat_farm2 by importing file "./results/02_dat_farm_v2.csv" 
# using read.csv function


```

### Create new datasets

```{r}
# create a new dataframe "dat_farm_rich" with data only from high-income country

# create a new dataframe "dat_farm_mid" with data only from mid-income country

# create a new dataframe "dat_farm_low" with data only from low-income country

```

### Summary statistics

```{r}
# dataframe structure using str() function

```

```{r}
# Use the stargazer function to generate well-formated summary statistics

```

## Simple plots

```{r}
# Histogram of yield for high-income country

# Histogram of yield for mid-income country

# Histogram of yield for low-income country

```

```{r}
# Scatterplots of yield vs. NPK


```

## Simple regression

### OLS

```{r}
# Run OLS separately for three income groups

```

## Export results

Since we created new variables, we might wish to save the new datasets into new csv files

```{r}
# Write data to csv file

```

Write summary statistics into txt file

```{r}
# Data summary statistics

```

Write the regression table into txt file

```{r}
# Regression results

```
